Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-04-24 WSSSPE1_report/WSSSPE1_summary_report.tex
finishing authors

\author{Daniel~S.~Katz$^{(1)}$,
Sou-Cheng~T.~Choi$^{(2)}$,
Hilmar~Lapp$^{(3)}$,
Ketan~Maheshwari$^{(4)}$,
Frank~Löffler$^{(5)}$,
Matthew~Turk$^{(6)}$,
Marcus~D.~Hanwell$^{(7)}$,
Nancy~Wilkins-Diehr$^{(8)}$,
James~Hetherington$^{(9)}$,
James~Howison$^{(10)}$,
%Shel~Swenson$^{(11)}$,
%Gabrielle~D.~Allen$^{(12)}$,
Bruce~Berriman$^{(11)}$
%Colin~Venters$^{(14)}$
}

\thanks{{}$^{(1)}$ National Science Foundation, Arlington, VA, USA; Computation Institute, University of Chicago \& Argonne National Laboratory, Chicago, IL, USA; \url{d.katz@ieee.org}}
%
\thanks{{}$^{(2)}$ NORC at the University of Chicago and   Illinois Institute of Technology, Chicago, IL, USA; \url{sctchoi@uchicago.edu}}
%
\thanks{{}$^{(3)}$ National Evolutionary Synthesis Center (NESCent),
  Durham, NC, USA; \url{hlapp@nescent.org}}
%
\thanks{{}$^{(4)}$ Argonne National Laboratory, Chicago, IL, USA; \url{ketan@anl.gov}}
%
\thanks{{}$^{(5)}$ Center for Computation and Technology, Louisiana State University, Baton Rouge, LA, USA; \url{knarf@cct.lsu.edu}}
%
\thanks{{}$^{(6)}$ Columbia Astrophysics Laboratory, Columbia University, New
York, NY, USA; \url{matthewturk@gmail.com}}
%
\thanks{{}$^{(7)}$ Scientific Computing Group, Kitware, Inc.,  Clifton Park, NY, USA; \url{marcus.hanwell@kitware.com}}
%
\thanks{{}$^{(8)}$ San Diego Supercomputer Center, University of California San Diego, La Jolla, CA, USA, \url{wilkinsn@sdsc.edu}}
%
\thanks{{}$^{(9)}$ Research Software Development Team, University College London, London, UK; \url {j.hetherington@ucl.ac.uk}}
%
\thanks{{}$^{(10)}$ University of Texas at Austin, Austin, TX, USA; \url{jhowison@ischool.utexas.edu}}
%
%\thanks{{}$^{(11)}$ xxx}
%
%\thanks{{}$^{(12)}$ xxx}
%
\thanks{{}$^{(11)}$ Infrared Processing and Analysis Center, California Institute of Technology, Pasadena, CA, USA; \url{gbb@ipac.caltech.edu}}
%
%\thanks{{}$^{(14)}$ xxx}

>>>>

\author{Daniel~S.~Katz$^{(1)}$,
Sou-Cheng~T.~Choi$^{(2)}$,
Hilmar~Lapp$^{(3)}$,
Ketan~Maheshwari$^{(4)}$,
Frank~L\"{o}ffler$^{(5)}$,
Matthew~Turk$^{(6)}$,
Marcus~D.~Hanwell$^{(7)}$,
Nancy~Wilkins-Diehr$^{(8)}$,
James~Hetherington$^{(9)}$,
James~Howison$^{(10)}$,
Shel~Swenson$^{(11)}$,
Gabrielle~D.~Allen$^{(12)}$,
Bruce~Berriman$^{(11)}$
Colin~Venters$^{(14)}$
}

\thanks{{}$^{(1)}$ National Science Foundation, Arlington, VA, USA; Computation Institute, University of Chicago \& Argonne National Laboratory, Chicago, IL, USA; \url{d.katz@ieee.org}}
%
\thanks{{}$^{(2)}$ NORC at the University of Chicago and   Illinois Institute of Technology, Chicago, IL, USA; \url{sctchoi@uchicago.edu}}
%
\thanks{{}$^{(3)}$ National Evolutionary Synthesis Center (NESCent),
  Durham, NC, USA; \url{hlapp@nescent.org}}
%
\thanks{{}$^{(4)}$ Argonne National Laboratory, Chicago, IL, USA; \url{ketan@anl.gov}}
%
\thanks{{}$^{(5)}$ Center for Computation and Technology, Louisiana State University, Baton Rouge, LA, USA; \url{knarf@cct.lsu.edu}}
%
\thanks{{}$^{(6)}$ Columbia Astrophysics Laboratory, Columbia University, New
York, NY, USA; \url{matthewturk@gmail.com}}
%
\thanks{{}$^{(7)}$ Scientific Computing Group, Kitware, Inc.,  Clifton Park, NY, USA; \url{marcus.hanwell@kitware.com}}
%
\thanks{{}$^{(8)}$ San Diego Supercomputer Center, University of California San Diego, La Jolla, CA, USA, \url{wilkinsn@sdsc.edu}}
%
\thanks{{}$^{(9)}$ Research Software Development Team, University College London, London, UK; \url {j.hetherington@ucl.ac.uk}}
%
\thanks{{}$^{(10)}$ University of Texas at Austin, Austin, TX, USA; \url{jhowison@ischool.utexas.edu}}
%
\thanks{{}$^{(11)}$ University of Illinois, Champaign, IL, USA; \url{gdallen@illinois.edu}}
%
\thanks{{}$^{(12)}$ University of Southern California, Los Angeles, CA, USA; \url{mdswenso@usc.edu}}
%
\thanks{{}$^{(11)}$ Infrared Processing and Analysis Center, California Institute of Technology, Pasadena, CA, USA; \url{gbb@ipac.caltech.edu}}
%
\thanks{{}$^{(14)}$ University of Huddersfield, Huddersfield, West Yorkshire, UK; \url{C.Venters@hud.ac.uk}}
